Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''

### 2025-07-04 writeUps/appendix.tex
(re)submitted online appendix

\documentclass[]{article}
\usepackage[letterpaper]{geometry}
\usepackage{xr}
\externaldocument{writeUps/paper}
\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage[caption=false]{subfig}
\usepackage[doublespacing]{setspace}

@@

\title{Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''}
%\runtitle{\textsc{geepers}}
%\maketitle

@@

\section*{Appendix: Proofs and Calculations}
\subsection*{Proof for Lemma \ref{lemma:expectation}}
As a preliminary, note that
% \begin{align*}
%   \EE[\st|\hpp]&=\EE\left\{\EE[\st|\pp,\hpp]|\hpp\right\}\\
%              &=\EE\left\{\EE[\st|\pp]|\hpp\right\}\\
%              &=\EE[\pp|\hpp]=\hpp
% \end{align*}

@@

\subsection*{Proof for Proposition \ref{prop:reg1}}

@@

\subsection*{A Stronger Version of Proposition \ref{prop:reg2} and a Proof}

@@

\subsection*{Sandwich Matrix Calculations}

@@

\subsection*{$A_{21}$ Matrix}
The estimating equations for the regression \eqref{eq:regression} are
\begin{equation}\label{eq:eeOLS}
  \psi(Y_i,\bxy_i,\bxsi,\bm{\beta},\alpha)=X_iY_i-X_iX_i'\bm{\beta}
\end{equation}
Where $X_i=[1,r_i,Z_i,r_iZ_i,\bxyt_i]'$.
In other words,
\begin{align*}
  \psi(Y_i,&\bxy_i,\bxsi,\bm{\beta},\bm{\alpha})=\\
  &\left\{
  \begin{array}{l}
    Y_i-\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)\\
    r_iY_i-r_i\left(\beta_0+\beta_2Z_i+\bm{\gamma}'\bxy_i\right)-r_i^2\left(\beta_1+\beta_3Z_i\right)\\
    Z_iY_i-Z_i\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)\\
    Z_ir_iY_i-Z_ir_i\left(\beta_0+\beta_2Z_i+\bm{\gamma}'\bxy_i\right)-Z_ir_i^2\left(\beta_1+\beta_3Z_i\right)\\
    \bxy_iY_i-\bxy_i\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)
  \end{array}
  \right\}
\end{align*}
(noting that $Z^2=Z$).
These depend on $\bm{\alpha}$ when $r_i=p_i$, i.e., when $Z_i=0$.% or $S_i$ is missing.
Then note that, following \eqref{eq:ps}, and letting $\eta_i=\bm{\alpha}'\bxsit$
\begin{equation}\label{eq:derivP}
  \frac{\partial p_i}{\partial \bm{\alpha}'}=f'(\eta_i)\frac{\partial \eta_i}{\partial \bm{\alpha}'}=f'(\eta_i)\bxsitp
\end{equation}
and that
\begin{equation}
  \frac{\partial p_i^2}{\partial \bm{\alpha}'}=2p_i\frac{\partial p_i}{\partial \bm{\alpha}'}=2f(\eta)f'(\eta_i)\bxsitp=2p_if'(\eta_i)\bxsitp
\end{equation}

@@

\clearpage

@@

\setcounter{page}{1}

\begin{center}
\large
    \textbf{Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''}
\end{center}
\section{Additional Simulation Results}
\subsection{Plot of  AUC versus $\alpha$}

\begin{center}

@@

\end{center}
%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}
\clearpage

\subsection{Full Empirical 95\% Interval Coverage Results}
The following tables give the empirical coverage of nominal 95\% intervals for \textsc{geepers} and mixture model principal effect estimates under varying data generating models. First we show results when $n=500$ per condition, and then when $n=1000$ per condition. \\

\begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=500$ per condition.}
  \input{writeUps/coverageTabAppendix500.tex}
 \end{table}

 \begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=1000$ per condition.}
  \input{writeUps/coverageTabAppendix1000.tex}
 \end{table}

\clearpage
\subsection{Full RMSE Results}
The following table gives the root mean squared error (RMSE), $\left\{\sum_b (\hat{\tau}-\tau)^2/500\right\}^{1/2}$, for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\

\begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=500$ per condition.}
  \input{writeUps/rmseTabAppendix500}
 \end{table}

 \begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=1000$ per condition.}
  \input{writeUps/rmseTabAppendix1000}
 \end{table}

%\end{table}
\clearpage

\section{Additional Results from the OPT Study}
\singlespacing
\subsection{Summary Statistics}
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

@@

\clearpage
\section{Additional Results from the Bottoming-Out Study}
\singlespacing
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

\subsection{Summary Statistics}
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\
\small
\input{tab1fac}
\clearpage

\small
\input{tab1num}

\subsection{Regression Results}
Regression estimates from three principal score logit models and three outcome regressions, based on the "All Covariates" principal score model, for \textsc{geepers} estimates. Standard errors shown are nominal regression errors, not sandwich corrected. Fixed-effect estimates for school (PS-models) or classroom (outcome models) are omitted.

\small
%\input{writeUps/outcomeRegAppendix}
\input{psTab}

@@

>>>>

\documentclass[]{article}
\usepackage[letterpaper]{geometry}
\usepackage{placeins}

\usepackage{xr}
\externaldocument{paper}
\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage[caption=false]{subfig}
\usepackage[doublespacing]{setspace}

@@

\title{Online Appendices for ``GEEPERs: Principal Stratification using
  Principal Scores and Stacked Estimating Equations''}
\date{}
%\runtitle{\textsc{geepers}}
\maketitle

@@

\section{Appendix: Proofs and Calculations}
\subsection{Proof for Lemma \ref{lemma:expectation}}
As a preliminary, note that
% \begin{align*}
%   \EE[\st|\hpp]&=\EE\left\{\EE[\st|\pp,\hpp]|\hpp\right\}\\
%              &=\EE\left\{\EE[\st|\pp]|\hpp\right\}\\
%              &=\EE[\pp|\hpp]=\hpp
% \end{align*}

@@

\subsection{Proof for Proposition \ref{prop:reg1}}

@@

\subsection{A Stronger Version of Proposition \ref{prop:reg2} and a Proof}

@@

\subsection{Sandwich Matrix Calculations}

@@

\subsection{$A_{21}$ Matrix}
The estimating equations for the regression \eqref{eq:regression} are
\begin{equation}\label{eq:eeOLS}
  \psi(Y_i,\bxy_i,\bxsi,\bm{\beta},\alpha)=X_iY_i-X_iX_i'\bm{\beta}
\end{equation}
Where $X_i=[1,r_i,Z_i,r_iZ_i,\bxyt_i]'$.
In other words,
\begin{align*}
  \psi(Y_i,&\bxy_i,\bxsi,\bm{\beta},\bm{\alpha})=\\
  &\left\{
  \begin{array}{l}
    Y_i-\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)\\
    r_iY_i-r_i\left(\beta_0+\beta_2Z_i+\bm{\gamma}'\bxy_i\right)-r_i^2\left(\beta_1+\beta_3Z_i\right)\\
    Z_iY_i-Z_i\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)\\
    Z_ir_iY_i-Z_ir_i\left(\beta_0+\beta_2Z_i+\bm{\gamma}'\bxy_i\right)-Z_ir_i^2\left(\beta_1+\beta_3Z_i\right)\\
    \bxy_iY_i-\bxy_i\left(\beta_0+\beta_1r_i+\beta_2Z_i+\beta_3Z_ir_i+\bm{\gamma}'\bxy_i\right)
  \end{array}
  \right\}
\end{align*}
(noting that $Z^2=Z$).
These depend on $\bm{\alpha}$ when $r_i=p_i$, i.e., when $Z_i=0$.% or $S_i$ is missing.
Then note that, following \eqref{eq:ps}, and letting $\eta_i=\bm{\alpha}'\bxsit$
\begin{equation}\label{eq:derivP}
  \frac{\partial p_i}{\partial \bm{\alpha}'}=f'(\eta_i)\frac{\partial \eta_i}{\partial \bm{\alpha}'}=f'(\eta_i)\bxsitp
\end{equation}
and that
\begin{equation}
  \frac{\partial p_i^2}{\partial \bm{\alpha}'}=2p_i\frac{\partial p_i}{\partial \bm{\alpha}'}=2f(\eta)f'(\eta_i)\bxsitp=2p_if'(\eta_i)\bxsitp
\end{equation}

@@

%\clearpage

@@

%\setcounter{page}{1}

% \begin{center}
% \large
%     \textbf{Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''}
%   \end{center}
  \FloatBarrier
\section{Additional Simulation Results}
\FloatBarrier
\subsection{Plot of  AUC versus $\alpha$}
\FloatBarrier
\begin{center}

@@

\end{center}
%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}
%\clearpage

\FloatBarrier
\subsection{Full Empirical 95\% Interval Coverage Results}
\FloatBarrier

The following tables give the empirical coverage of nominal 95\% intervals for \textsc{geepers} and mixture model principal effect estimates under varying data generating models. First we show results when $n=500$ per condition, and then when $n=1000$ per condition. \\

\begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=500$ per condition.}
  \input{coverageTabAppendix500.tex}
 \end{table}

 \begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=1000$ per condition.}
  \input{coverageTabAppendix1000.tex}
 \end{table}

%\clearpage
\FloatBarrier
\subsection{Full RMSE Results}
\FloatBarrier

The following table gives the root mean squared error (RMSE), $\left\{\sum_b (\hat{\tau}-\tau)^2/500\right\}^{1/2}$, for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\

\begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=500$ per condition.}
  \input{rmseTabAppendix500}
 \end{table}

 \begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=1000$ per condition.}
  \input{rmseTabAppendix1000}
 \end{table}

%\end{table}
%\clearpage

\FloatBarrier
\section{Additional Results from the OPT Study}
\FloatBarrier
\singlespacing
\FloatBarrier
\subsection{Summary Statistics}
\FloatBarrier
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

@@

%\clearpage
\FloatBarrier
\section{Additional Results from the Bottoming-Out Study}
\singlespacing
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

\FloatBarrier
\subsection{Summary Statistics}
\FloatBarrier

The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\
\small
\input{tab1fac}
%\clearpage

\small
\input{tab1num}
\FloatBarrier
\subsection{Regression Results}
\FloatBarrier

Regression estimates from three principal score logit models and three outcome regressions, based on the "All Covariates" principal score model, for \textsc{geepers} estimates. Standard errors shown are nominal regression errors, not sandwich corrected. Fixed-effect estimates for school (PS-models) or classroom (outcome models) are omitted.

\small
%\input{outcomeRegAppendix}
\input{psTab}

@@

\bibliographystyle{apalike}
\bibliography{MOM}
